Frequentist Statistic

### 2017-06-08 frequentist_statistics/frequentist_statistics.Rmd
minor typo

Note that the formula listed in this section is used when the **two groups are independent of one another (not paired)**. e.g. If we wish to compare pre- (beginning of semester) and post-test (end of semester) scores of students, then this will require a paired t-test.

@@

- [Coursera: Inference Statistics](https://www.coursera.org/learn/inferential-statistics-intro)
- [Blog: What Are P-Values?](https://prateekvjoshi.com/2013/12/07/what-are-p-values/)
- [Blog: One-way Analysis of Variance](http://www.r-bloggers.com/one-way-analysis-of-variance-anova/)
- [Blog: The Theorem Every Data Scientist Should Know](http://www.jeannicholashould.com/the-theorem-every-data-scientist-should-know-2.html)
- [Notes: Power and sample size calculation for t test in R](http://users.stat.umn.edu/~corbett/classes/3022/Power_and%20_sample_size_for_t_in_R.txt)

>>>>

Note that the formula listed in this section is used when the **two groups are independent of one another (not paired)**. e.g. If we wish to compare pre- (beginning of semester) and post-test (end of semester) scores of students, then this will require a **paired t-test**. The following video explains it nicely. [Youtube: The Paired-Difference t Procedure](https://www.youtube.com/watch?v=TMRBGFIj0RM)

@@

- [Coursera: Inference Statistics](https://www.coursera.org/learn/inferential-statistics-intro)
- [Blog: What Are P-Values?](https://prateekvjoshi.com/2013/12/07/what-are-p-values/)
- [Blog: One-way Analysis of Variance](http://www.r-bloggers.com/one-way-analysis-of-variance-anova/)
- [Blog: The Theorem Every Data Scientist Should Know](http://www.jeannicholashould.com/the-theorem-every-data-scientist-should-know-2.html)
- [Youtube: The Paired-Difference t Procedure](https://www.youtube.com/watch?v=TMRBGFIj0RM)
- [Notes: Power and sample size calculation for t test in R](http://users.stat.umn.edu/~corbett/classes/3022/Power_and%20_sample_size_for_t_in_R.txt)
